---
title: "R collection"
author: "meeting"
date: "2020/5/2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## __Vector__ 
> 1. __simple patterned vectors__

- construct a vecctor
  
seq()中的參數by指每個數字個0.5; 參數length.out指將數字範圍平分成幾個區塊段
```{r}
seq(1, 5)
rep(3, 12)
```

先用NA建一個空的vector會比較清楚
```{r}
a <- c(3,5,9,10)
V <- rep(NA, 7)
V[1:4] <- a
V
```
- unique()回傳所有不重複的元素
```{r}
b <- c(3, 3, 3, 3, 5, 5, 1, 2, 10, 10, 8)
unique(b)
```
- table()計算vector中的元素各有幾個
```{r}
table(b)
```
- union()為聯集
`B <- c(3, 1, 5, 4, 7)`
`C <- c(23, 1, 44, 5, 3)`
```{r, echo=FALSE}
B <- c(3, 1, 5, 4, 7)
C <- c(23, 1, 44, 5, 3)
```

```{r}
union(B, C)
```
- intersect()
```{r}
intersect(B, C)
```
- sort(x, decreasing = False, ...) 回傳排序後的元素

`a <- c(3, 4, 2, 7, 10, 23, 8, 9, 11)`
```{r,echo=FALSE}
a <- c(3, 4, 2, 7, 10, 23, 8, 9, 11)
```
```{r}
sort(a)
sort(a, decreasing = TRUE)
```
- order(..., na.list = TRUE, decreasing = FALSE) 回傳排序後的元素`編號`
```{r}
order(a)
order(a, decreasing = TRUE)
```
- __changing__ values in a vector can
```{r}
a[5] <- -3
a[8] <- -1
a
```
- __deleting__ element from a vector

  刪掉該位置的元素
```{r}
a[-2]
a[-c(3:6)]
```
- __“is.”__ series

is.integer
is.numeric
is.double
is.character
```{r}
is.null(c())
x1 <- 1:5
x3 <- colors
c(is.integer(x1), is.numeric(x1), is.double(x1))
c(is.character(x3), is.numeric(x3))

```

as.numeric
```{r}
c(TRUE, FALSE, T, F)
c(3<5, 3>5, 3==5, 3!=5)
logical <- c(3<5, 3>5, 3==5, 3!=5)
logical
logical == TRUE
as.numeric(logical)
sum(logical == TRUE)  ## logical裡有幾個TRUE
sum(logical)  ## 相當於sum(logical == TRUE)
```

is.na
```{r}
B <- c(2, NA, 5 , 10)
is.na(B)
# TRUE
which(is.na(B))
which(is.na(B) == 1)
ind.T <- which(is.na(B))
B1 <- B[-ind.T]
B1
# FALSE
which(!is.na(B))
which(is.na(B) == 0)
```
__<Example 1>__
```{r}
A <- c(3, 4, NA, 12, 0.2, NA, -2)
B <- c(3, 5, "red", 4, NA)
# (1)
is.numeric(A)
is.numeric(B)
# (2)
sum(is.na(A))
sum(is.na(B))
# (3)
which(is.na(A))
which(is.na(B))
# (4)
which(A < 1)
which(B < 1)
which(B < 5)
```
- class
```{r}
a <- c(3, 4, 2, 7, 10, 23, 8, 9, 11)
b <- c("red", "yellow", "blue")
c <- c(TRUE, FALSE)
c(class(a), class(b), class(c))
```

- - -
## __matrix__
> 1. __construct a matrix__

  - rbind中每個數列代表一列;cbind中每個數列代表一行
```{r}
a <- 1:5; b <- 6:10;
c <- 11:15; d <- 16:20
M1 <- rbind(a,b,c,d)
M1
M2 <- cbind(a,b,c,d)
M2
```
- `X <- 1:20`
```{r, echo=FALSE}
X <- 1:20
```

```{r}
matrix(X, nrow = 4, ncol = 5)
matrix(X, nrow = 5, ncol = 4)
```


```{r}
matrix(X, nrow = 4, ncol = 5, byrow = TRUE)
matrix(X, nrow = 5, ncol = 4, byrow = TRUE)
```
> 2. features for a matrix

```{r}
M1
```

```{r}

dim(M1)
colnames(M1);rownames(M1)
colnames(M1) <- c("V1", "V2", "V3", "V4", "V5")
dimnames(M1)
```


- Extract elements from a matrix

取M1中的第2列第4行的元素
```{r}
M1[2, 4]
```

```{r}
M1[c(2, 4), 3]
M1[c(2, 4), c(3, 5)]
M1[c(2,3), ]
M1[c("b", "c"), ]
M1[5] #M1[1,2]
```

> 3. Evaluation of Matrix

- statistics description

```{R}
A <- matrix(c(1:5, 7:10), 3, 3)
A
colSums(A)
rowSums(A)
colMeans(A)
rowMeans(A)
```
- transpose
```{r}
t(A)
```
- calculation
```{r}
diag(A)
det(A)
```
-   $A^{-1}$ is an inverse matrix of A: $AA^{−1} = I$
```{r}
solve(A)
```
- eigen system
```{r}
D <- matrix(rnorm(9), 3, 3)
eig.D <- eigen(D)
eig.D$values
eig.D$vectors
```


4. 
$\left[
\begin{array}{cc}
A & B \\
C & D \\
\end{array}
\right]$

- - -
## __Control Flow__

> 1. The for() loop

    `for (index in vector) commands`

- notes
  - for迴圈很浪費資源 不一定會比較快
  - 多多善用vector
- __<Example 1>__

Construct a vector as Xn+1 = 2Xn + 3,where X0 = 3, n = 1, 2, 3, 4, 5, 6, 7
```{r}
vec.X.v1 <- c()
Xn <- 3
for(n in 1:7){
Xn <- 2*Xn + 3
vec.X.v1 <- c(vec.X.v1, Xn)
}
vec.X.v1
```

- __<Example 2>__
  
n! = n ∗ (n − 1) ∗ (n − 2) ∗ · · · ∗ 2 ∗ 1
```{r}
# Try n = 10.
n <- 10
ans <- 1
for(j in n:1){
ans <- ans * j
}
ans
factorial(n)

```
- __<Example 3>__

Find the first 12 values in the Fibonacci sequence.
Let F1 = 1 and F2 = 1.

Fn+2 = Fn+1 + Fn, n = 1, 2, 3, ..., 10
```{r}
f1 <- 1
f2 <- 1
all <- rep(NA, 12)
all[1] <- f1
all[2] <- f2
for(n in 3:12){
  k = f1+f2
  f1 <- f2
  f2 <- k
  all[n] <- k
}
all
```


> 2. The if() statement

`if (condition) {commands when TRUE}`
`if (condition) {commands when TRUE} else {commands when FALSE}`

- __<Example 1>__
```{r}
a <- 2
b <- 2
if(a == b){
  a*b
  c <- a*b
} else if(a==2){
  c <- 2
} else{
  c <- a+b
}
# R裡的空格沒有意義

if(a==b) c <- a*b
# if只有一個敘述且沒有else才能這樣寫
```

- __<Example 2>__

Given C = {3, 5, NA, 12, 0.2, NA, −2}, find the locations of NA
```{r}
C <- c(3, 4, NA, 12, 0.2, NA, -2)
for(i in 1:7){
if(is.na(C[i])) print(i)
}
```
```{r}
na.loc <- c()
for(i in 1:7){
if(is.na(C[i])) 
  na.loc <- c(na.loc, i)
}
na.loc

```

> 3. The while() loop

`while (condition) statements`
```{r}
j <- 1
while(j <= 8){
print(j)
j <- j + 1
}
```
- __<Example 1>__

Rolling a fair dice, evaluate the total number that all possible outcomes
occur at least once. Start from the seed 20191025.
Use sample(1:6, 1) to simulate a outcome of rolling a fair dice.
```{r}
runif(1)
set.seed(20200503)
t <- c()
while (length(unique(t)) < 6){
  X <- sample(1:6, 1)
  t <- c(t, X)
}

length(t)
```

> 4. break & repeat & next

- break
`if (condition) break`

- repeat
`repeat { statements }`

- next

- - -
## __Function__

> 1. source()

`print( ) shows with " " between characters.`
`cat() shows without " " between characters.`
```{r}
x <- c("A", "B", "C", "D")
print(x)
cat(x)
```
> 2. function()

- __<Example 1>__

$f (x) = 3x + 2, x=2,3,4$

```{r}
f <- function(x){
3*x + 2
}
f(2)
```
- `return` in the function()
```{r}
f <- function(x){
res <- 3*x + 2
}
f(2)
# return nothing
```
```{r}
f <- function(x){
res <- 3*x + 2
return (res) # return the output
}
f(2)
```

> 3. list

`$: the name of the element.`
`[[ ]]: the location or the name of the element.`

- __<Example 1>__
```{r}
X <- list(a = 3, b = c(1:5), c = c("A", "B"))
X
```
```{r}
X$a
X[[2]]
X[["c"]]
```

- creat a list
```{r}
try.list <- list() ## a null list
length(try.list)
length(try.list) <- 2 ## assign the size to the list
try.list[[1]] <- seq(0, 10, length.out = 3) ## without name
try.list$square <- seq(0, 10, length.out = 3)^2 ## with name
try.list
```


> 4. Use `invisible( )` to hide some output.

```{r}
perfect.number <- function(a, b){
k <- a
res <- c()
ans <- list()
while(k < b){
fac <- c()
for(j in 1:k){
if((k %% j) == 0) fac <- c(fac, j)
}
if(k == sum(fac[-length(fac)])) {
res <- c(res, k)
ans[[paste(k)]] <- fac[-length(fac)]
}
k <- k+1
}
print(res)
ans$number <- res
return(invisible(ans)) # do not show the output
}
```

- - - 

## __Data Frame__

> 1. __`data.frame()`__

- __<Example 1>__

```{r}
colors <- c("red", "yellow", "blue")
numbers <- c(1, 2, 3)
colors.and.numbers <- data.frame(colors, numbers,
more.numbers = c(4, 5, 6))
colors.and.numbers
```
- __difference with matrix__
    - These are like matrices, but with the columns having their own names.
    - Columns can be of different types from each other.

> 2. __types in a data frame: chracter__

Change the type from factor to character by using `stringAsFactors =FALSE`
```{r}
colors <- c("red", "yellow", "blue")
numbers <- c(1, 2, 3)
colors.and.numbers <- data.frame(colors, numbers,
more.numbers = c(4, 5, 6),
stringsAsFactors = FALSE)
str(colors.and.numbers)
```
> 3. add rows/columns

  - row: use `rbind()`
  - column: use the sign `$` or `cbind()`
```{r}
data2 <- data.frame(colors, numbers, more.numbers = c(4, 5, 6),
stringsAsFactors = FALSE)
data2 <- rbind(data2, c("black", 4, 7))
data2$new.column <- c('a','b','c','d')
data2
```
> 4. Data input and output at hard disk

- Change the directory: __`setwd(“dir”)`__
- Find the directory: __`get()`__
- To save all objects in the current workspace, type __`save.image(“XXX.RData”)`__
- To save parts of objects, type __`save(a, b, c, file = “XXX.RData”)`__ 
- Use __`load(“XXX.RData”)`__ to retrieve data.
- Save data to a file
  - __`write.table(A, file = “XXX.txt”)`__
  - __`write.csv(A, file = “XXX.csv”)`__
- Read data from a file
  - __`read.table(file = “XXX.txt”)`__
  - __`read.csv(file = “XXX.csv”)`__

> 5. R Package

- To download a package, type __`install.packages(“XXX”)`__
- Before using some functions in a downloaded package, you should call
the package by typing __`library(XXX)`__

> 6. Tools for help
- typee __`help(name)`__ or __`?name`__

- - -
## __R Graphics__
> 1. Graphics for descriptive statistics

- Histogram: hist(x)
```{r}
x.norm <- rnorm(100, mean=0, sd=1)
hist(x.norm)
```
- Boxplot: boxplot(x)
```{r}
boxplot(x.norm)
```
- Density plot: plot(density(x))
```{r}
plot(density(x.norm))
```
- Barchart: barplot(x)
```{r}
x <- sample(c(1:8), 100, replace=TRUE, prob=c(8:1))
x <- table(x)
names(x) <- c("A", "B", "C", "D", "E", "F", "G", "H")
barplot(x)
```
- Piechart: pie(x)
```{r}
pie(x)
```

- plot(x, y)
```{r}
x <- rnorm(100)
y <- 3*x + rnorm(100, 0, 1)
plot(x, y)
cor(x, y)

```
- Scatter plots for multiple variables: pairs(...)
```{r}
X <- matrix(rnorm(30), 10, 3) ## use matrix
pairs(X, pch = 19)
```
- Boxplot for multiple categories: boxplot(x)
```{r}
X <- data.frame(group = rep(c("A", "B", "C", "D", "E"), each = 10),
res = rnorm(50))
boxplot(res ~ group, data = X)
```
> 2. general plot function: plot(...)

```{D3}
par(mfrow = c(2,3)) # split plot ranges
plot(x, y,
type = "p", ### types of the plot
pch = , ### the symbol in the plot
main = NULL, ### the title of the plot
lty = , ### the style of a line
lwd = , ### the width of a line
cex = , ### the size of an text
bty="o", ### the box around the plot
col = , ### the color of an object
xlim = NULL, ylim = NULL, # the range of an axis
sub = NULL, ### the sub-title of the plot
xlab = NULL, ylab = NULL, # the name of an axis
cex.main = ### the size of the title
)
```
```{r}
type = c("p", "l", "b", "s", "o", "h", "n")
```
“p”: points
“l”: lines
“b”: both points and lines
“o”: lines pass through points
“h”: the lines between points and x-axis
“n”: no content in the plot but plot region “‘

- notes
  - par()：擺放圖的排法
- - -

## __Apply family__

> 1. __`apply(X, MARGIN, FUN,...)`__

Returns a vector or array or list of values obtained by applying a function to margins of an array or a matrix
- __<Example 1>__
```{r}
A <- matrix(rnorm(1500), 500, 3)

apply(A, 2, sum); colSums(A)
```
- __<Example 2>__
```{r}
apply(A, 2, max)
apply(A, 2, min, na.rm = TRUE)
```

- What if there are NA’s?
```{r}
B <- matrix(sample(1:100, 15), 5, 3)
B[1, 2] <- NA
B[3, 1] <- NA
B <- data.frame(B)
colnames(B) <- c("factor 1", "factor 2", "factor 3")
apply(B, 2, mean)
apply(B, 2, mean, na.rm = TRUE)

```
> 2. __`lapply(X, FUN,...)`__

Returns a list of the same length as X, each element of which is the result of applying
FUN to the corresponding element of X

- __<Example 1>__
```{r}
C <- list(a = 1:10, beta = exp(-3:3))
lapply(C, mean)
```
```{r}
par(mfrow = c(1, 2))
lapply(C, hist)
```
> 3. __`sapply(X, FUN,..., simplify = TRUE)`__

```{r}
sapply(C, summary, simplify = FALSE)
```
- Similarlly to lapply(X, Fun,...) if sapply(x, f, simplify = FALSE, USE.NAMES = FALSE)
```{r}
sapply(C, summary, simplify = FALSE)
lapply(C, summary)
```

- - - 
## __About Data__

> 1. Remove NA

- is.na(X)
- complete.cases(X)
```{r}
no.na <- complete.cases(airquality)
head(airquality[no.na,])
```
```{r}
dat.no.na.1 <- airquality[no.na,]
dim(dat.no.na.1)
```

- na.omit(X):
```{r}
dat.no.na.2 <- na.omit(airquality)
dim(dat.no.na.2)
```
> 2. Using __`cut(...)`__ to group or to label items

```{r}
grouped2 <- cut(airquality[,3], 5,
labels = c("G1", "G2", "G3", "G4", "G5"))
head(grouped2)
```
  - Summarize the number of each group
```{r}
airquality$group <- grouped2
table(grouped2)

```
  - order the dataset by the group: __`order(...)`___
```{r}
order.data.1 <- airquality[order(airquality$group),]
head(order.data.1)
```
```{r}
order.data.2 <- airquality[order(airquality$group,
airquality$Temp), ]
head(order.data.2)
```

> 3. Package: reshape2

```{r}
game <- c("G1", "G2", "G3", "G4", "G5")
site <- c("M", "O", "L", "O", "L")
Lin <- c(15, 6, 26, 22, 18)
Jordan <- c(18, 32, 21, 25, 12)
Peter <- c(10, 6, 22, 9, 12)
ballgames <- data.frame(game, site, Lin, Jordan, Peter)
```
- Use __`melt(data, id.vars)`__ to reshape the dataset.
```{r}
library(reshape2)
melt(ballgames, id.vars = c("game", "site"))

```
- Use __`dcast(dataset, formula, fun)`__ to show the specific data format.

> 4. Merge data: __`merge(...)`__
- intersection
  - `merge(Lin.game, Jordan.game)`

- union
  - `merge(Lin.game, Jordan.game, all = TRUE)`


> 5. Regression

- Regression is used to show the relationship between independent variables and
dependent variables.
- Before data analysis, we should check the relation plot
```{r}
pairs(airquality[,c(1,3,4)])
```

- linear model: __`lm(formula, data)`__
  
  - formula: y ~ x1 + x2 (with intercept)
  - formula: y ~ x1 + x2 - 1(no intercept)

```{r}
data1 <- airquality[1:120, ]
data2 <- airquality[121:153, ]
lm1 <- lm(Ozone ~ Temp, data = data1)
lm2 <- lm(Ozone ~ Temp - 1, data = data1)
```
- Prediction by the fitted linear model
```{r}
y.predict <- predict(lm1, data2)
y.predict
```

  - Performance of fitted model
```{r}
plot(airquality[, 4], airquality[, 1], pch = 19)
abline(lm1)
points(airquality[121:153, 4], y.predict, col = 2, pch = 19)
```
 
  - Performance of prediction
```{r}
plot(airquality[121:153, 1], y.predict, pch = 19)
abline(0, 1)

```

> 6. Package: dplyr

__`%>%`__ means that apply functions to an object.
```{r}
library(dplyr)
y <- sample(1:100, 10)
mean(y)
y %>% mean()
min(y)
y %>% min()
```

## __Data processing__

- __<Example 1>__
```{r}
train <- read.csv(file = "C:/Users/Meeting/Documents/R/reliability_training.csv")
#getwd()
head(train['Unit.ID'][1])
f1 <- sum(train['Unit.ID']=="F1")
f2 <- sum(train['Unit.ID']=="F2")
f3 <- sum(train['Unit.ID']=="F3")
f4 <- sum(train['Unit.ID']=="F4")
f5 <- sum(train['Unit.ID']=="F5")
f1+f2+f3+f4+f5
t <- 1
for (i in train['Unit.ID']){
  t <-sum(i=="F5")
}
t
```

- __<Example 2>__

A pair of fair dice are to be continually rolled until all the possible outcomes 2, 3, . . ., 12 have
occurred at least once. Develop a function to collect the total number of rolls. Conduct the code for
10000 times and give the average of the 10000 rolls. Is it possible that the total number of rolls is 11?
How many times do you get the result that the number of rolls is 11? (You should use the following
two functions.)
```{r}
times <- function(n){
  roll <- c()
  for (k in 1:n){
    i <- 1
    Sum <- c()
    while (length(unique(Sum)) < 11){
      X <- sample(1:6, 1)
      Y <- sample(1:6, 1)
      Sum <- c(Sum, sum(X,Y))
      i <- i+1
      if (i > n)break
    }
    roll <- c(roll, i)
  }
  return (mean(roll))
}
times(10000)
```


